

\subsubsection{Discrete Time}
$P(X_{n+1} = j | X_n = i_n , X_{n-1} = i_{n-1}, ... , X_0 = i_0)$

\paragraph{Markov Chain Assumption}
$P(X_{n+1} = j | X_n = i_n )$, Applying total probability
$P(X_{n+1} = j ) = \sum_{i} P(X_{n+1} = j |  X_n = i_n) P(X_n = i)$

\paragraph{Homogeneous Markov Chain}
$P(X_{n+1} = j | X_n = i_n ) = p_{ij} \quad \forall i,j$ (IE: independant of n)

\paragraph{Chapman-Kolmogorov Equation}
Let $p_{ij}^(m)$ be the probability of starting from state i and arriving at state j in m steps.
$p_{ij}^{(m)} = \sum_k p_{ik} p_{kj}^{(m-1)} = \sum_k p_{ik}^{(m-1)}p_{kj}$

\paragraph{Irreducible Markov Chain} Every state can be reached from every other state.

\paragraph{Recurrence}
Let $f_j^{(n)}$ be the probability of first returning to j occurs n steps after leaving j. \\
Let $f_j = \sum_{n=1}^\infty f_j^{(n)}$, then
state is recurrent $\iff f_j = 1$

\paragraph{Recurrent Non-null}
Let $M_j = \sum_{n=1}^\infty n f_j^{(n)}$ then state j is recurrent non-null
$\iff M_j <<< \infty$. Otherwise, it's recurrent null.

\paragraph{Periodicity} The number of steps to come back is $cn$, where $c > 1$

\paragraph{State Probability}
Let $\pi_j^{(n)} = P(X_n = j)$

\paragraph{Homogenerous State Probability}
$\pi_j^{(n+1)} = \sum_j p_{ij} \pi_i^{(n)}$. Given all $\pi_j^{(0)}$, you can
compute any state.

\paragraph{Steady State Probability} If aperiodic irreducible homogeneous Markov
Chain then $\pi_j = \lim_{n \to \infty} \pi_j^{(n)}$ and can be computed using
the system of equations:
\begin{align*}
	\pi_j = \sum_i p_{ij} \pi_i \quad \forall j \\
	\sum_i \pi_j = 1
\end{align*}

\paragraph{Memoryless Property} Residence time in a state has the memoryless
property. The prob you state m steps, and leave on the $(j+1)^{th}$ is
$p_{jj}^m(1-p_{jj})$. This has the memoryless property.

\subsubsection{Continuous Time}

\paragraph{Transistion Probability}
\begin{align*}
	P_{ij}(v,t) &= P(X(t) = j | X(v) = i) \\
	P_{ij}(t,t) &=
	\left\{
		\begin{alignedat}{3}
			& 1  & \qquad & \mbox{if } i=j \\
			& 0  & \qquad & \mbox{if } i=j
		\end{alignedat}
	\right. \\
	q_{kj}(t) &= \lim_{\triangle t \to 0} \frac{P_{kj}(t,t+\triangle t)}{\triangle t} \\
	q_{jj}(t) &= \lim_{\triangle t \to 0} \frac{P_{jj}(t,t+\triangle t)-1}{\triangle t} \\
	\frac{ \partial P_{ij}(v,t) }{ \partial t }
	&= \sum_{k\ne j} P_{ij}(v,t) q_{kj}(t) + P_{ij}(v,t) q_{jj}(t) \\
\end{align*}

\paragraph{State Probability}
\begin{align*}
	\pi_j(t) = P(X(j) = j) \\
	\pi_j(t) = \sum_i P_{ij}(v,t) \pi_i(v) \\
	\frac{d \pi_j(t)}{dt} = \sum_i \frac{ \partial P_{ij}(v,t)}{\partial t} \pi_i(v) \\
	\frac{d \pi_j(t)}{dt} = \sum_{k\ne j} \pi_k(v) q_{kj}(t) + \pi_j(v) q_{jj}(t)  \\
\end{align*}

\paragraph{Homogeneous State Probability}
$\frac{d \pi_j(t)}{dt} = \sum_{k\ne j} \pi_k(v) q_{kj} + \pi_j(v) q_{jj}$

\paragraph{Steady State}
\begin{align*}
	\pi_j = \lim_{t \to \infty} \pi_j(t) \\
	\Rightarrow \frac{ d \pi_j(t)}{dt} =  \frac{ d \pi_j }{dt} = 0 \\
\end{align*}
Can solve steady state using the (j+1) equations:
\begin{align*}
	\sum_{k \ne j } \pi_k q_{kj} + \pi_j q_{jj} = 0 \qquad \forall j \\
	\sum_j \pi_j = 1
\end{align*}

\paragraph{Residence Time in State is Memoryless} How long will we stay in state
j, given we have already stayed for s amount of time.
\begin{align*}
	P( R_j > s + t | R_j > s) = P(R_j > t)
\end{align*}


\subsubsection{Birth Death Process}
\begin{align*}
	q_{j,j+1} &= \lambda_j & j \ge 0 \\
	q_{j,j-1} &= \mu_j & j \ge 1 \\
	q_{j,j}   &= -(\lambda_j + \mu_j) & j \ge 0 \\
	q_{i,j}   &= 0 &  |i-j| \ge 2
\end{align*}
\paragraph{Steady State} system of equations
\begin{align*}
	\frac{\lambda_j}{\mu_j} &< 1 \qquad \mbox{for } j \ge j_0  \mbox{ then steady state converges }\\
	p_0 &= \frac{1}{1 + \sum_{j=1}^\infty \prod_{i=0}^{j-1} \frac{\lambda_i}{\mu_{i+1}}} \\
	p_j &= \left ( \prod_{i=0}^{j-1} \frac{\lambda_{i}}{\mu_{i+1}} \right ) p_0 \qquad j \ge 1
\end{align*}

\paragraph{Performance Metrics}
\begin{align*}
	\lambda_E = \sum_{j=0}^\infty \lambda_j p_j \\
	Y = \lambda_E \\
	Q = \sum_{j=1}^\infty j p_j \\
	R = \frac{Q}{\lambda_E}
\end{align*}

\paragraph{Solving Process}
\begin{tabular}{ c | c c c c c}
	i           & 0           & 1           & 2           & ...\\
	\hline
	$\lambda_i$ & $\lambda_0$ & $\lambda_1$ & $\lambda_2$ & ... \\
	$\mu_{i+1}$ & $\mu_1$     & $\mu_2$     &  $\mu_3$    & ... \\
\end{tabular}

\subsubsection{Kendall Notation}
\paragraph{M/M/N} n servers working in parallel, drawing from same queue
\paragraph{M/M/$\infty$} No queue. When job arrives, there is a server available
to process it.
\paragraph{M/M/1/K} System can only have K jobs in the system. The $(K+1)^{th}$
job gets regected.
\paragraph{M/M/1/$\infty$/N} Finite population model with N user work stations.
\subsubsection{State Transistion Rate Diagram}
\paragraph{Flow In = Flow Out}
\paragraph{Mean Value Analysis (Finite Population Model)}
\begin{align*}
	Q_i(0) &= 0 \\
	R_i(n) &= \frac{1}{\mu_i}[ 1 + Q_i(n-1) ] \\
	V_i    &= \frac{\lambda_i}{\lambda_0} \\
	R(n)   &= \sum_i V_i R_i \\
	Y(n)   &= \frac{N}{Z+R(n)} \\
	Q_i(n) &= Y(n) V_i R_i(n)
\end{align*}
\paragraph{Closed Network Model} Insert 'server 0' wih N users = N ciruclating
jobs. Z (mean think time) = 0. Apply MVA as stated above.





